Left-linear rules in adhesive categories

### 2024-02-14 icalp/fusione.tex
typo

\begin{definition}[Graph signature]
  Let $\mathcal{G}=(V, E, s, t)$ be a finite directed acyclic graph,
  we define the \emph{depth} of a vertex $v\in V$ as
  way:
  \[
    \dph(v)=\begin{cases}
      0 & \text{there is no $e\in E$ such that $t(e)=v$}\\
      m+1 &\text{where } m=\min\{\dph(s(e)) \mid e\in E \text{ such that } t(e)=v
      \} 
    \end{cases}
  \]
\end{definition}

>>>>

\begin{definition}[Graph signature]
  Let $\mathcal{G}=(V, E, s, t)$ be a finite directed acyclic graph,
  we define the \emph{depth} of a vertex $v\in V$ as
  \[
    \dph(v)=\begin{cases}
      0 & \text{there is no $e\in E$ such that $t(e)=v$}\\
      m+1 &\text{where } m=\min\{\dph(s(e)) \mid e\in E \text{ such that } t(e)=v
      \} 
    \end{cases}
  \]
\end{definition}
